\section{Simple Booklink Fixture}

This file intentionally has three source-map targets spread across a long file.

TeX filler before alpha 001.
TeX filler before alpha 002.
TeX filler before alpha 003.
TeX filler before alpha 004.
TeX filler before alpha 005.
TeX filler before alpha 006.
TeX filler before alpha 007.
TeX filler before alpha 008.
TeX filler before alpha 009.
TeX filler before alpha 010.
TeX filler before alpha 011.
TeX filler before alpha 012.
TeX filler before alpha 013.
TeX filler before alpha 014.
TeX filler before alpha 015.
TeX filler before alpha 016.
TeX filler before alpha 017.
TeX filler before alpha 018.
TeX filler before alpha 019.
TeX filler before alpha 020.
TeX filler before alpha 021.
TeX filler before alpha 022.
TeX filler before alpha 023.
TeX filler before alpha 024.
TeX filler before alpha 025.
TeX filler before alpha 026.
TeX filler before alpha 027.
TeX filler before alpha 028.
TeX filler before alpha 029.
TeX filler before alpha 030.
TeX filler before alpha 031.
TeX filler before alpha 032.
TeX filler before alpha 033.
TeX filler before alpha 034.
TeX filler before alpha 035.
TeX filler before alpha 036.
TeX filler before alpha 037.
TeX filler before alpha 038.
TeX filler before alpha 039.
TeX filler before alpha 040.
TeX filler before alpha 041.
TeX filler before alpha 042.
TeX filler before alpha 043.
TeX filler before alpha 044.
TeX filler before alpha 045.

% BOOKLINK-START lean=SimpleFixture.alpha_theorem kind=statement
\begin{theorem*}[Alpha theorem]
Alpha theorem statement starts here.
It proves alpha.
\end{theorem*}
% BOOKLINK-END lean=SimpleFixture.alpha_theorem kind=statement

TeX filler between alpha and beta 001.
TeX filler between alpha and beta 002.
TeX filler between alpha and beta 003.
TeX filler between alpha and beta 004.
TeX filler between alpha and beta 005.
TeX filler between alpha and beta 006.
TeX filler between alpha and beta 007.
TeX filler between alpha and beta 008.
TeX filler between alpha and beta 009.
TeX filler between alpha and beta 010.
TeX filler between alpha and beta 011.
TeX filler between alpha and beta 012.
TeX filler between alpha and beta 013.
TeX filler between alpha and beta 014.
TeX filler between alpha and beta 015.
TeX filler between alpha and beta 016.
TeX filler between alpha and beta 017.
TeX filler between alpha and beta 018.
TeX filler between alpha and beta 019.
TeX filler between alpha and beta 020.
TeX filler between alpha and beta 021.
TeX filler between alpha and beta 022.
TeX filler between alpha and beta 023.
TeX filler between alpha and beta 024.
TeX filler between alpha and beta 025.
TeX filler between alpha and beta 026.
TeX filler between alpha and beta 027.
TeX filler between alpha and beta 028.
TeX filler between alpha and beta 029.
TeX filler between alpha and beta 030.
TeX filler between alpha and beta 031.
TeX filler between alpha and beta 032.
TeX filler between alpha and beta 033.
TeX filler between alpha and beta 034.
TeX filler between alpha and beta 035.
TeX filler between alpha and beta 036.
TeX filler between alpha and beta 037.
TeX filler between alpha and beta 038.
TeX filler between alpha and beta 039.
TeX filler between alpha and beta 040.
TeX filler between alpha and beta 041.
TeX filler between alpha and beta 042.
TeX filler between alpha and beta 043.
TeX filler between alpha and beta 044.
TeX filler between alpha and beta 045.
TeX filler between alpha and beta 046.
TeX filler between alpha and beta 047.
TeX filler between alpha and beta 048.
TeX filler between alpha and beta 049.
TeX filler between alpha and beta 050.
TeX filler between alpha and beta 051.
TeX filler between alpha and beta 052.
TeX filler between alpha and beta 053.
TeX filler between alpha and beta 054.
TeX filler between alpha and beta 055.
TeX filler between alpha and beta 056.
TeX filler between alpha and beta 057.

% BOOKLINK-START lean=SimpleFixture.beta_prose
Some prose target says beta words exactly here.
% BOOKLINK-END lean=SimpleFixture.beta_prose

TeX filler between beta and gamma 001.
TeX filler between beta and gamma 002.
TeX filler between beta and gamma 003.
TeX filler between beta and gamma 004.
TeX filler between beta and gamma 005.
TeX filler between beta and gamma 006.
TeX filler between beta and gamma 007.
TeX filler between beta and gamma 008.
TeX filler between beta and gamma 009.
TeX filler between beta and gamma 010.
TeX filler between beta and gamma 011.
TeX filler between beta and gamma 012.
TeX filler between beta and gamma 013.
TeX filler between beta and gamma 014.
TeX filler between beta and gamma 015.
TeX filler between beta and gamma 016.
TeX filler between beta and gamma 017.
TeX filler between beta and gamma 018.
TeX filler between beta and gamma 019.
TeX filler between beta and gamma 020.
TeX filler between beta and gamma 021.
TeX filler between beta and gamma 022.
TeX filler between beta and gamma 023.
TeX filler between beta and gamma 024.
TeX filler between beta and gamma 025.
TeX filler between beta and gamma 026.
TeX filler between beta and gamma 027.
TeX filler between beta and gamma 028.
TeX filler between beta and gamma 029.
TeX filler between beta and gamma 030.
TeX filler between beta and gamma 031.
TeX filler between beta and gamma 032.
TeX filler between beta and gamma 033.
TeX filler between beta and gamma 034.
TeX filler between beta and gamma 035.
TeX filler between beta and gamma 036.
TeX filler between beta and gamma 037.
TeX filler between beta and gamma 038.
TeX filler between beta and gamma 039.
TeX filler between beta and gamma 040.
TeX filler between beta and gamma 041.
TeX filler between beta and gamma 042.
TeX filler between beta and gamma 043.
TeX filler between beta and gamma 044.
TeX filler between beta and gamma 045.
TeX filler between beta and gamma 046.
TeX filler between beta and gamma 047.
TeX filler between beta and gamma 048.
TeX filler between beta and gamma 049.
TeX filler between beta and gamma 050.
TeX filler between beta and gamma 051.
TeX filler between beta and gamma 052.
TeX filler between beta and gamma 053.
TeX filler between beta and gamma 054.
TeX filler between beta and gamma 055.
TeX filler between beta and gamma 056.
TeX filler between beta and gamma 057.

% BOOKLINK-START lean=SimpleFixture.gamma_proof
\begin{proof}[Proof]
Gamma proof step happens here.
\end{proof}
% BOOKLINK-END lean=SimpleFixture.gamma_proof

TeX filler after gamma 001.
TeX filler after gamma 002.
TeX filler after gamma 003.
TeX filler after gamma 004.
TeX filler after gamma 005.
TeX filler after gamma 006.
TeX filler after gamma 007.
TeX filler after gamma 008.
TeX filler after gamma 009.
TeX filler after gamma 010.
TeX filler after gamma 011.
TeX filler after gamma 012.
TeX filler after gamma 013.
TeX filler after gamma 014.
TeX filler after gamma 015.
TeX filler after gamma 016.
TeX filler after gamma 017.
TeX filler after gamma 018.
TeX filler after gamma 019.
TeX filler after gamma 020.
TeX filler after gamma 021.
TeX filler after gamma 022.
TeX filler after gamma 023.
TeX filler after gamma 024.
TeX filler after gamma 025.
TeX filler after gamma 026.
TeX filler after gamma 027.
TeX filler after gamma 028.
TeX filler after gamma 029.
TeX filler after gamma 030.
TeX filler after gamma 031.
TeX filler after gamma 032.
TeX filler after gamma 033.
TeX filler after gamma 034.
TeX filler after gamma 035.
TeX filler after gamma 036.
TeX filler after gamma 037.
TeX filler after gamma 038.
TeX filler after gamma 039.
TeX filler after gamma 040.
TeX filler after gamma 041.
TeX filler after gamma 042.
TeX filler after gamma 043.
TeX filler after gamma 044.
TeX filler after gamma 045.
